A Real-Time Sonar Simulator for Automatic Target Recognition

### 2019-06-22 Simulator/article.tex
2019-05-19
2019-06-05
2019-06-21

\usepackage{accents}

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
   \usepackage[pdftex,
    final,                %Keep hyperlink stuff even when in draft mode
    breaklinks=true,      %Break links when necessary
    linktocpage=true,     %Enable link to page?
    linkcolor=black,  %Colour of links to labels within document
    citecolor=black,      %Colour of links to the biliography
    filecolor=red,        %Colour of links to local files
    pagecolor=black,        %Colour of links to other pages withing document
    urlcolor=Blue,        %Colour of the links to external URLs
    colorlinks=true,      %??
    plainpages=false,     %Store roman/arabic numbering differently to avoid
    bookmarksnumbered ]{hyperref}
% 
% \else
%    \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}%
\fi
%    \usepackage{breakurl}                        % Allows 'dvips' driver to break links

@@

\usepackage{tikz}
\usetikzlibrary{calc,positioning,shapes,snakes}
%\newcommand{\tikzmark}[1]{\tikz[remember picture]\coordinate(#1){(-.35em,-.545ex)};}
\newcommand{\tikzmark}[2]{\tikz[remember picture,baseline=(#1.base)]\node[shape=rectangle,inner sep=0pt](#1){#2};}
\newcommand*\circled[1]{\tikz[baseline=(char.base)]{
            \node[shape=circle,draw,inner sep=2pt] (char) {#1};}}

\usepackage{multirow}
\usepackage{tabularx}

@@

@@

>>>>

\usepackage{accents}
\usepackage{moresize}

% NOTE: PDF hyperlink and bookmark features are not required in IEEE
%       papers and their use requires extra complexity and work.
% \newcommand\MYhyperrefoptions{bookmarks=true,bookmarksnumbered=true,
% pdfpagemode={UseOutlines},plainpages=false,pdfpagelabels=true,
% colorlinks=true,linkcolor={black},citecolor={black},urlcolor={black},
% pdftitle={Optimal Window Design for the Low Complexity Adaptive Beamformer in Active Sonar Imaging},
% pdfsubject={},
% pdfauthor={Jo Inge Buskenes},
% pdfkeywords={adaptive beamforming, beamforming, complexity, sonar, active}}%
\ifCLASSINFOpdf
%    \usepackage[\MYhyperrefoptions,pdftex]{hyperref}
   \usepackage[pdftex,
    final,                %Keep hyperlink stuff even when in draft mode
    breaklinks=true,      %Break links when necessary
    linktocpage=true,     %Enable link to page?
    linkcolor=black,  %Colour of links to labels within document
    citecolor=black,      %Colour of links to the biliography
    filecolor=red,        %Colour of links to local files
    pagecolor=black,        %Colour of links to other pages withing document
    urlcolor=Blue,        %Colour of the links to external URLs
    colorlinks=true,      %??
    plainpages=false,     %Store roman/arabic numbering differently to avoid
    unicode=true,
    bookmarksopen=true,
%    bookmarksopenlevel=3,
    bookmarksnumbered=false ]{hyperref}
% 
% \else
%    \usepackage[\MYhyperrefoptions,breaklinks=true,dvips]{hyperref}%
\fi
%    \usepackage{breakurl}                        % Allows 'dvips' driver to break links

@@

% Exotic orchids
% https://visme.co/blog/wp-content/uploads/2016/01/63-1024x512.jpg
%\definecolor{cDarkBlue}{HTML}{192e5b}
%\definecolor{cBlue}{HTML}{1d65a6}
%\definecolor{cLightBlue}{HTML}{73a2c0}
%\definecolor{cGreen}{HTML}{00743f}
%\definecolor{cYellow}{HTML}{f2a104}
%\colorlet{cBase}{cLightBlue}
%\colorlet{cBaseMark}{cGreen}
%\colorlet{cPoint}{cYellow}
%\colorlet{cBasis}{cDarkBlue}

%\titleformat{\subsubsection}[hang]{\itshape}{\thesubsubsection}{0.6em}{}

%\makeatletter
%\xpatchcmd{\@sect}{%
%  \protected@edef\@svsec{\@seccntformat{#1}\relax}%
%}{%
%  \ifnum0=\pdfstrcmp{#1}{section}%
%  \def\@svsec{\circlednumber{\number\value{section}}\quad\relax}%
%  \else
%  \protected@edef\@svsec{\@seccntformat{#1}\relax}%
%  \fi
%  }{}{}
%\makeatother

%\titleformat{\subsubsection}{\Large\bfseries}{}{0em}{%
%\begin{picture}(0,0)
%\put(12,4){\circle{28}}
%\end{picture}\makebox[1.45em][c]{\thesubsubsection}\quad}

\usepackage{multirow}
\usepackage{tabularx}
\usepackage{collcell}
\usepackage{booktabs}
\usepackage{calc}
%\usepackage{ifthen}

@@

\usepackage{listings}
%\usepackage[outputdir=build]{minted}

\lstset{
  %These 3 parameters should be re-specified for each listing:
   language=bash%
 , caption=%
 , label=%
% , extendedchars=false
%%  , inputencoding=utf8
%  %
%%  ,  fancyvrb=false % Beamer hates fancyvrb
%%   morecomment=[1]\ ,
%%   fvcmdparams=<\frac><2>,
% , backgroundcolor=\color{codeBackground}%
%  %
 , basicstyle=\small
% , keywordstyle=\color{DarkBlue}%
%% , identifierstyle=\color{green}%
% , commentstyle=\color{ForestGreen}\itshape%
%  %morecomment=[|]{//}
% , stringstyle=\color{Brown}%
%  %
%% , showspaces=false%
%% , showstringspaces=false%
%% , showtabs=false%
%  %
%% , frame=single                            %single, shadowbox, framed
 , frame=bt
%%  , xtopmargin=0pt%
%%  , xbottommargin=0pt%
%% , framesep=20pt
%% , rulesep=20pt
%% , lineskip=1ex
 , aboveskip=\baselineskip % space above listing
 , belowskip=\baselineskip % space below listing
 , framexleftmargin=1em%
% , framexrightmargin=0pt%
% , linewidth=\linewidth%
 , xleftmargin=1em%        %To vertically align the box with the rest of the text in the
% , xrightmargin=0em%       %document, rather than having the text aligned and the box overshoot.
% , tabsize=2%
% , abovecaptionskip=1\baselineskip
% , belowcaptionskip=0pt
%  %  
 , captionpos=b%     %Caption at bottom
%  % 
% , breaklines=true%  
% , breakatwhitespace=false%
%  %
 , mathescape=true%
%% , literate=*{-}{-}1
% , columns=fullflexible
%% , float
%% , extendedchars=false
%% , escapeinside={\$}{\$}
%%   escapebegin={|},
%%   escapeend={|},
%% , inputencoding=utf8x
%  %
%% , numbers=left%
%% , numberstyle=\tiny\color{SeaGreen}%
%% , stepnumber=1%
%% , numbersep=2em 
 }

@@

%% Cool blues (sea)
%\definecolor{deep_aqua}{HTML}{003b46}
%\definecolor{ocean}{HTML}{07575b}
%\definecolor{wave}{HTML}{66a5ad}
%\definecolor{sea_foam}{HTML}{c4dfe6}
%\colorlet{base}{wave}
%\colorlet{bright}{ocean}
%\colorlet{dark}{deep_aqua}
%
%% Invigorating
%% https://visme.co/blog/wp-content/uploads/2016/01/26-1024x512.jpg
%\definecolor{cDarkBlue}{HTML}{003b46}
%\definecolor{cBlue}{HTML}{07575b}
%\definecolor{cLightBlue}{HTML}{66a5ad}
%\definecolor{cYellow}{HTML}{c4dfe6}
%\definecolor{cRed}{HTML}{c4dfe6}
%\colorlet{base}{wave}
%\colorlet{bright}{ocean}
%\colorlet{dark}{deep_aqua}

%% Invigorating
%% https://visme.co/blog/wp-content/uploads/2016/01/26-1024x512.jpg
%\definecolor{cBlue}{HTML}{80add7}
%\definecolor{cGreen}{HTML}{0abda0}
%\definecolor{cWhite}{HTML}{ebf2ea}
%\definecolor{cYellow}{HTML}{d4dca9}
%\definecolor{cBrown}{HTML}{bf9d7a}
%\colorlet{cBase}{cBlue}
%\colorlet{cBaseMark}{cGreen}
%\colorlet{cPoint}{cYellow}
%\colorlet{cBasis}{cBrown}
